Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-09-11 Manuscript/manuscript.tex
Updated caption in the validation figure (x-ray form f and order params) with chem structure of POPC.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.0cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.eps}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Order parameters of head group, glycerol backbone and sn-1 and sn-2 tails  from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{There seems to a typo in experimental value for other order parameter for C2 carbon in sn-2 chain; it should be negative.
    The scale of the y-axis should be then zoomed when this is fixed.} \\
  \todo{I would put the acyl chain order parameters also for original Lipid14; JOE: Already done, check whether your figures are up to date. I usually push only *.eps.}\\
  \todo{x-axis scale in form factor figure would be better from 0 to 0.6. The experimental data is available for this range.} \\
  \todo{$S_{CD} -> S_{CH}$}
\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.5cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.eps}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: chemical structure of POPC with definitions of headgroup order parameters.
    Middle: Order parameters of head group, glycerol backbone and sn-1 and sn-2 tails  from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.
    Bottom: X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    }
\end{figure}
